Linting Linearity in Core/System FC

### 2023-01-09 report.tex
Introduction on linear types

@@

\section{Linear Types}

@@

@@

\section{Core Haskell}

>>>>

Linear type systems\cite{} add expressiveness to existing type systems by
defining that linear resources must be used exactly once (linearly). In
programming languages with a linear type system, not using certain resources or
using them twice are type errors. Linear types can, thus, be used, e.g., to
guarantee file handles, socket descriptors and allocated memory are freed
exactly once (leaks and double-frees become type errors)\cite{}, implement safe
high-performance language interop\cite{}, guarantee quantum entangled states are
not duplicated~\cite{}, handle mutable state\cite{}, a bit on session
types guarantees\cite{}, and much more.

% TODO: Also include bit about how it makes the basis of other type systems such
% as rusts owneship. How ?

As an example, consider the following program which allocates some memory and
frees it twice. The variable $p$ is a linear resource created by the
\textbf{malloc} keyword.

\begin{code}
let p = malloc 4
 in free p
    free p
\end{code}

Because $p$ is a linear variable, it must be used exactly once. However, we are
using it in both calls to \textbf{free}. The example program doesn't typecheck!
In section~\ref{linear-types} we describe the fundamentals of linear types in
more detail with a formal definition and many examples.

Despite their usefulness, most mainstream programming languages don't have
linear types. In practice, it can be hard to balance linear and non-linear types
and avoid the boilerplate threading of linear resources that we'll see ahead.

% The main contributions of this thesis are:
% \begin{itemize}
%     \item Core Type system which accepts optimized linear programs
% \end{itemize}

% stores a value to the allocated memory, reads from it and finally frees

% Linear type systems add expressiven at the type level regarding values that
% must be used exactly once thorought their lifetime.

% about the usage of resources in a
% programming language.

\section {Introduction}

A história que eu quero contar:

@@

\section{Linear Types\label{linear-types}}

Programming languages with linear type systems might differ in their definition of linear
resources, but usually \emph{variables} are considered linear resources
% That is, we can rely on the type system to prove properties regarding the usage of certain resources.
The \emph{Hello World} of linearly typed programs is a linearly typed pointer.
In a non-memory managed language, an allocated pointer must be freed
\emph{exactly once}.

\begin{code}
let p = malloc(5)
    p' = store(p, "x")
    (p'', v) = load(p)
    free p''
\end{code}

% We'd like to hide the boilerplate involved \cite{Linear constraints}

In order to give well defined semantics to a linear type system, we present a
linearly typed lambda calculus which is a very simple language with linear
types.

@@

\subsection{Linear Haskell}

@@

\subsection{Core Haskell}
